\section{Preface}

Beginnings aren’t simple; they take courage and curiosity. Courage to try something new is applauded, whether what is new is a new profession, such as  identity management, or a new discipline, such as learning federation after already mastering access certification. Regardless, setting out to do something new requires the curiosity to figure out how to do it.

A consistent challenge in our profession is finding the resources from which to learn that new thing. IDPro’s mission is to help do just that: connecting professionals to learn from one another, providing opportunities to learn from experts, and building resources from which professionals can learn. And this bibliography is one such resource.

The collation of suggestions from identity professionals, this bibliography hopes to provide a needed resource for people with the courage and curiosity to begin something. The books, blogs, and articles referenced within span a wide range of topics and a wide range of approaches. And more that than, it offers a glimpse as to why your peers suggested the resource in the first. Knowing why someone read something is a useful clue as to the value you’ll get from reading the same thing.

This bibliography represents a beginning in and of itself. It is the first, of what will be many resources, that our Body of Knowledge Committee has created. I applaud the group for their courage and curiosity to begin and hope you find a gem or two in here that helps you on your beginning!

\vspace{24pt}
{\setlength{\parindent}{0cm}
\textsc{
January 10, 2019\\
Ian Glazer\\
Founder and President, IDPro}
}
